Transfer learning between Sentinel-1 acquisition modes enhances \\ the few-shot segmentation of natural oil slicks in the Arctic

### 2025-04-01 latex/manuscript.tex
fig1 small fix

Image processing to align SAR images is crucial to ensure transferable, high-level features between the source and the target domain—here interferometric-wide (IW) and extra-wide (EW) Sentinel-1 images.
Given these conditions, both deep learning models benefited from transferring pretrained model weights, with DeepLab performing best overall although SAM achieves top accuracy with fewer training images.
The analysis was validated using two documented seeps in the Arctic, where further research could potentially identify additional, undiscovered occurrences. 
Overall, our findings highlight the potential of transfer learning. This approach remains underutilized in remote sensing, yet it is promising for addressing data scarcity, 
with practical applications such as monitoring natural seepage in remote marine environments.

>>>>

Image processing to align SAR images is crucial to ensure transferable, high-level features between the source and the target domain—here interferometric-wide (IW) and extra-wide (EW) Sentinel-1 images.
Given these conditions, both deep learning models benefited from transferring pretrained model weights, with DeepLabv3 performing best overall although SAM achieved top accuracy with fewer training images.
The analysis was validated using two documented seeps in the Arctic, where further research could potentially identify additional, undiscovered occurrences. 
Overall, our findings highlight the potential of transfer learning. This approach remains underutilized in remote sensing, yet it is promising for addressing data scarcity, 
with practical applications such as monitoring natural seepage in remote marine environments.
